CrypTool Script\footnote{ Background reading for the CrypTool program}\\ Mathematics and Cryptography

### 2003-05-23 script/de/chapters/primes.tex
be update

% $Id$
% ...........................................................................
%                             P R I M Z A H L E N
% /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

\hypertarget{FermatNumbers01}{}
Fermat\index{Fermat} hatte im 17. Jahrhundert an Mersenne \index{Mersenne Marin} geschrieben, dass er vermute, 
dass alle Zahlen der Form $$ F(n) = 2^{2^n} + 1 $$ f"ur alle ganzen Zahlen $n$ gr"o"ser 
oder gleich $0$ prim seien (\hyperlink{FermatNumbers02}{siehe unten},
Kapitel~\ref{spezialzahlentypen}).
\index{Zahlen!Fermatzahl}\index{Fermat!Fermatzahl}

@@

Ein st"arkerer Test stammt von\index{Miller}\index{Rabin}
Miller/Rabin: er wird nur von sogenannten {\em starken
Pseudoprimzahlen} bestanden. Wiederum gibt es starke
Pseudoprimzahlen, die keine Primzahlen sind, aber das passiert
deutlich seltener als bei den (einfachen) Pseudoprimzahlen. Die
kleinste starke Pseudoprimzahl zur Basis $2$ ist
$$ 15.841 = 7 \cdot 31 \cdot 73. $$
Testet man alle 4 Basen $2, 3, 5$ und $7$, so findet man bis $25 \cdot 10^9$
nur eine starke Pseudoprimzahl, also eine Zahl, die den Test besteht und doch keine Primzahl ist.

@@

\vskip +15 pt
\hypertarget{FermatNumbers02}{}
\item {\em Fermatzahlen}\footnote{Die Fermatschen Primzahlen spielen unter
       anderem eine wichtige Rolle in der Kreisteilung. Wie Gauss \index{Gauss}
       bewiesen hat, ist das regul"are $p$-Eck f"ur eine Primzahl $p>2$ dann
       und nur dann mit Zirkel und Lineal konstruierbar, wenn $p$ eine 
       Fermatsche Primzahl ist.}
   \index{Zahlen!Fermatzahl}\index{Fermat!Fermatzahl}  $F(m) = 2^{2^m} + 1$:\\
    Wie \hyperlink{FermatNumbers01}{oben} erw"ahnt, schrieb Fermat an 
    Mersenne, dass er vermutet, dass alle Zahlen dieser Form prim seien. 
    Erstaunlicherweise w"are es f"ur ihn m"oglich gewesen, mit dem auf 
    seinem kleinen Satz beruhenden negativen Primzahltest f"ur $n=5$ ein 
    positives Ergebnis zu erhalten.
$$
\begin{array}{lll}
F(0) = 2^{2^0} + 1  = 2^1 + 1 & = 3 &   \mapsto {\rm ~prim}  \\
F(1) = 2^{2^1} + 1  = 2^2 + 1 & = 5 &   \mapsto {\rm ~prim}  \\
F(2) = 2^{2^2} + 1  = 2^4 + 1 & = 17 &  \mapsto {\rm ~prim}  \\
F(3) = 2^{2^3} + 1  = 2^8 + 1 & = 257 & \mapsto {\rm ~prim}  \\
F(4) = 2^{2^4} + 1  = 2^{16} + 1 &  = 65.537 &  \mapsto {\rm ~prim}  \\
F(5) = 2^{2^5} + 1  = 2^{32} + 1 &  = 4.294.967.297 = 641 \cdot
6.700.417 &  \mapsto {\rm ~NICHT~prim} !\\
F(6) = 2^{2^6} + 1  = 2^{64} + 1 &  = 18.446.744.073.709.551.617 \\
                                 &  = 274.177 \cdot 67.280.421.310.721  
																 & \mapsto {\rm ~NICHT~prim} ! \\
F(7) = 2^{2^7} + 1  = 2^{128} + 1 & = \mbox{(siehe S.~\pageref{f7})}  
																 & \mapsto {\rm ~NICHT~prim} !

@@

\item Polynomfunktionen $f(x) = a_n x^n + a_{n-1}x^{n-1} + \cdots + 
    a_1 x^1 + a_0$  ($a_i$ aus ${\mathbb Z}$, $n \geq 1$):

@@

\pagebreak
\item \index{Catalan} \index{Catalanzahlen} Catalan, nach dem auch die sog. {\em Catalanzahlen} $A(n) = (1 / (n+1) ) * (2n)! / (n!)^2$ benannt sind,
    "au"serte die Vermutung, dass $C_4$ eine Primzahl ist:
$$
\begin{array}{l}
C_0 = 2, \\
C_1 = 2^{C_0} - 1,  \\
C_2 = 2^{C_1} - 1,  \\
C_3 = 2^{C_2} - 1, \\
C_4 = 2^{C_3} - 1, \cdots \\
\end{array}
$$
\begin{sloppypar}
    (siehe
        {\href{http://www.utm.edu/research/primes/mersenne.shtml}{\tt http://www.utm.edu/research/primes/mersenne.shtml}}
        unter Conjectures and Unsolved Problems).
\end{sloppypar}

@@

Dies ist der \index{Primzahlsatz} \textbf{Primzahlsatz} (prime
number theorem). Er wurde von Legendre (1752-1833) \index{Legendre} und Gauss\index{Gauss}
(1777-1855) aufgestellt und erst "uber 100 Jahre sp"ater bewiesen.

@@

Primzahlzwillinge sind Primzahlen, die den Abstand 2 voneinander haben, zum Beispiel 5 und 7 oder
101 und 103. Primzahldrillinge gibt es dagegen nur eines: 3, 5, 7.  Bei allen anderen Dreierpacks
aufeinanderfolgender ungerader Zahlen ist immer eine durch 3 teilbar und somit keine Primzahl.
\begin{itemize}
  \item Offen ist die Anzahl der Primzahlzwillinge: unendlich viele oder eine begrenzte Anzahl?
  Das bis heute bekannte gr"o"ste Primzahlzwillingspaar ist
  $1.693.965 \cdot 2^{66.443} \pm 1.$
  \item Gibt es eine Formel f"ur die Anzahl der Primzahlzwillinge pro Intervall?
  \item Der Beweis oben zu der Funktion  $f: \: N \rightarrow Z$ mit $n \mapsto a^{3^n}$  garantiert nur die Existenz einer
    solchen Zahl $a$.  Wie kann diese Zahl $a$ bestimmt werden, und wird sie einen Wert haben, so dass
    die Funktion auch von praktischem Interesse ist?
  \item Gibt es unendlich viele Mersenne-Primzahlen?\index{Primzahl!Mersenne}\index{Mersenne!Mersenne-Primzahl}
  \item Gibt es unendlich viele Fermatsche Primzahlen?
  \item Gibt es einen Polynomialzeit-Algorithmus zur Zerlegung einer Zahl in ihre Primfaktoren (vgl.
    \cite[S. 167]{Klee1997})?
    Diese Frage kann man auf die beiden folgenden Fragestellungen aufsplitten:
  \begin{itemize}
        \item Gibt es einen Polynomialzeit-Algorithmus, der entscheidet, ob eine Zahl prim ist?
        \item Gibt es einen Polynomialzeit-Algorithmus, mit dem sich f"ur eine zusammengesetzte Zahl $n$ ein
        nicht-trivialer (d.h. von $1$ und von $n$ verschiedener) Teiler von $n$ berechnen l"asst?\footnote{Vergleiche auch Kapitel \ref{RSABernstein} und Kapitel \ref{NoteFactorisation}.}
        \end{itemize}
\end{itemize}

@@

\item Den besten "Uberblick zu Primzahlen (weil sehr aktuell und vollst"andig)
      bieten m.E.  ~\glqq The Prime Pages\grqq~ von Chris Caldwell.
      \index{Chris Caldwell} \\
      \href{http://www.utm.edu/research/primes}
       {\tt http://www.utm.edu/research/primes }

>>>>

% $Id$
% ...........................................................................
%       K A P I T E L  2 :     P R I M Z A H L E N
% /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

\hypertarget{FermatNumbers01}{}%
Fermat\index{Fermat Pierre} hatte im 17. Jahrhundert an Mersenne \index{Mersenne Marin} geschrieben, dass er vermute, 
dass alle Zahlen der Form $$ F(n) = 2^{2^n} + 1 $$ f"ur alle ganzen Zahlen $n$ gr"o"ser 
oder gleich $0$ prim seien (\hyperlink{FermatNumbers02}{siehe unten},
Kapitel~\ref{spezialzahlentypen}).
\index{Zahlen!Fermatzahl}\index{Fermat!Fermatzahl}

@@

Ein st"arkerer Test stammt von\index{Miller G.L.}\index{Rabin}
Miller/Rabin: er wird nur von sogenannten {\em starken
Pseudoprimzahlen} bestanden. Wiederum gibt es starke
Pseudoprimzahlen, die keine Primzahlen sind, aber das passiert
deutlich seltener als bei den (einfachen) Pseudoprimzahlen. Die
kleinste starke Pseudoprimzahl zur Basis $2$ ist
$$ 15.841 = 7 \cdot 31 \cdot 73. $$
Testet man alle 4 Basen $2, 3, 5$ und $7$, so findet man bis $25 \cdot 10^9$
nur eine starke Pseudoprimzahl, also eine Zahl, die den Test besteht und doch keine Primzahl ist.

@@

\vskip +15 pt
\hypertarget{FermatNumbers02}{}
\item {\em Fermatzahlen}\footnote{Die Fermatschen Primzahlen spielen unter
       anderem eine wichtige Rolle in der Kreisteilung. 
       Wie Gauss \index{Gauss Carl Friedrich}
       bewiesen hat, ist das regul"are $p$-Eck f"ur eine Primzahl $p>2$ dann
       und nur dann mit Zirkel und Lineal konstruierbar, wenn $p$ eine 
       Fermatsche Primzahl ist.}
   \index{Zahlen!Fermatzahl}\index{Fermat!Fermatzahl}  $F(m) = 2^{2^m} + 1$:\\
    Wie \hyperlink{FermatNumbers01}{oben} erw"ahnt, schrieb Fermat an 
    Mersenne, dass er vermutet, dass alle Zahlen dieser Form prim seien. 
    Erstaunlicherweise w"are es f"ur ihn m"oglich gewesen, mit dem auf 
    seinem kleinen Satz beruhenden negativen Primzahltest f"ur $n=5$ ein 
    positives Ergebnis zu erhalten.
$$
\begin{array}{lll}
F(0) = 2^{2^0} + 1  = 2^1 + 1 & = 3 &   \mapsto {\rm ~prim}  \\
F(1) = 2^{2^1} + 1  = 2^2 + 1 & = 5 &   \mapsto {\rm ~prim}  \\
F(2) = 2^{2^2} + 1  = 2^4 + 1 & = 17 &  \mapsto {\rm ~prim}  \\
F(3) = 2^{2^3} + 1  = 2^8 + 1 & = 257 & \mapsto {\rm ~prim}  \\
F(4) = 2^{2^4} + 1  = 2^{16} + 1 &  = 65.537 &  \mapsto {\rm ~prim}  \\
F(5) = 2^{2^5} + 1  = 2^{32} + 1 &  = 4.294.967.297 = 641 \cdot
6.700.417 &  \mapsto {\rm ~NICHT~prim} !\\
F(6) = 2^{2^6} + 1  = 2^{64} + 1 &  = 18.446.744.073.709.551.617 \\
                                 &  = 274.177 \cdot 67.280.421.310.721  
																 & \mapsto {\rm ~NICHT~prim} ! \\
F(7) = 2^{2^7} + 1  = 2^{128} + 1 & = \mbox{(siehe S.~\pageref{f7})}  
																 & \mapsto {\rm ~NICHT~prim} !

@@

\item Polynomfunktionen\index{Polynom} $f(x) = a_n x^n + a_{n-1}x^{n-1} + \cdots + 
    a_1 x^1 + a_0$  ($a_i$ aus ${\mathbb Z}$, $n \geq 1$):

@@

\pagebreak
\item \index{Catalan Eugene} \index{Catalan-Zahlen} Eugene Charles Catalan\footnote{%
Belgischer Mathematiker, 30.5.1814-14.2.1894. Nach ihm sind auch die 
sogenannten {\em Catalan-Zahlen}
$A(n) = (1 / (n+1) ) * (2n)! / (n!)^2  =  1, 2, 5, 14, 42, 132, 429, 1430, 
4862, 16796, 58786, 208012, 742900, 2674440, 9694845, ... $
benannt.}
"au"serte die Vermutung, dass $C_4$ eine Primzahl ist:
$$
\begin{array}{l}
C_0 = 2, \\
C_1 = 2^{C_0} - 1,  \\
C_2 = 2^{C_1} - 1,  \\
C_3 = 2^{C_2} - 1, \\
C_4 = 2^{C_3} - 1, \cdots \\
\end{array}
$$
\begin{sloppypar}
    (siehe
        {\href{http://www.utm.edu/research/primes/mersenne.shtml}{\tt http://www.utm.edu/research/primes/mersenne.shtml}}
        unter Conjectures and Unsolved Problems).
\end{sloppypar}

@@

Dies ist der \index{Primzahlsatz} \textbf{Primzahlsatz} (prime
number theorem). Er wurde von Legendre\footnote{%
Adrien-Marie Legendre, Französischer Mathematiker, 18.9.1752$-$10.1.1833.
}
\index{Legendre Adrien-Marie}
und Gauss\index{Gauss Carl Friedrich} (1777-1855) aufgestellt und 
erst "uber 100 Jahre sp"ater bewiesen.

@@

Primzahlzwillinge sind Primzahlen, die den Abstand 2 voneinander haben, zum Beispiel 5 und 7 oder
101 und 103. Primzahldrillinge gibt es dagegen nur eines: 3, 5, 7.  Bei allen anderen Dreierpacks
aufeinanderfolgender ungerader Zahlen ist immer eine durch 3 teilbar und somit keine Primzahl.
\begin{itemize}
  \item Offen ist die Anzahl der Primzahlzwillinge: unendlich viele oder eine begrenzte Anzahl?
  Das bis heute bekannte gr"o"ste Primzahlzwillingspaar ist
  $1.693.965 \cdot 2^{66.443} \pm 1.$
  \item Gibt es eine Formel f"ur die Anzahl der Primzahlzwillinge pro Intervall?
  \item Der Beweis oben zu der Funktion  $f: \: N \rightarrow Z$ mit $n \mapsto a^{3^n}$  garantiert nur die Existenz einer
    solchen Zahl $a$.  Wie kann diese Zahl $a$ bestimmt werden, und wird sie einen Wert haben, so dass
    die Funktion auch von praktischem Interesse ist?
  \item Gibt es unendlich viele Mersenne-Primzahlen?\index{Primzahl!Mersenne}\index{Mersenne!Mersenne-Primzahl}
  \item Gibt es unendlich viele Fermatsche Primzahlen?
  \item Gibt es einen Polynomialzeit-Algorithmus\index{Polynom} zur Zerlegung einer Zahl in ihre Primfaktoren (vgl.
    \cite[S. 167]{Klee1997})?
    Diese Frage kann man auf die beiden folgenden Fragestellungen aufsplitten:
  \begin{itemize}
        \item Gibt es einen Polynomialzeit-Algorithmus, der entscheidet, ob 
	      eine Zahl prim ist?
	      Diese Frage wurde durch den AKS-Algorithmus\index{AKS} 
	      beantwortet (vgl.  Kapitel\ref{PrimesinP}, ``Primes in P'':
	      Testen auf Primalit"at ist polynominal).
        \item Gibt es einen Polynomialzeit-Algorithmus, mit dem sich f"ur eine zusammengesetzte Zahl $n$ ein
        nicht-trivialer (d.h. von $1$ und von $n$ verschiedener) Teiler von $n$ berechnen l"asst?\footnote{Vergleiche auch Kapitel \ref{RSABernstein} und Kapitel \ref{NoteFactorisation}.}
        \end{itemize}
\end{itemize}

@@

\item Den besten "Uberblick zu Primzahlen (weil sehr aktuell und vollst"andig)
      bieten m.E.  ~\glqq The Prime Pages\grqq~ von Chris Caldwell.
      \index{Caldwell Chris} \\
      \href{http://www.utm.edu/research/primes}
       {\tt http://www.utm.edu/research/primes }

### 2003-05-23 script/en/chapters/cryptomethods.tex
be update

% --------------------------------------------------------------------------
\subsubsection{New results about cryptanalysis of AES}
\index{Cryptanalysis}

@@

% --------------------------------------------------------------------------
\subsubsection{Current status of brute-force attacks on 
symmetric algorithms (RC5)}
\index{brute-force attack}
\index{RC5}

@@

The most well-known asymmetric procedure is the \index{RSA} 
RSA algorithm\index{CrypTool}%
\footnote{%
The RSA algorithm is extensively described in chapter 3.10 and later
within this script. 
The RSA cryptosystem can be executed in many variations with 
CrypTool\index{CrypTool} v1.3 (using the menu 
{\bf Individual Procedures \textbackslash{} RSA Demonstration \textbackslash{}
RSA Cryptosystem}). 
The topical research results concerning RSA are described in chapter 3.11.
}%
,
named after its developers Ronald \index{Rivest Ronald} Rivest, Adi
\index{Shamir Adi} Shamir and Leonard \index{Adleman Leonard} Adleman. The RSA algorithm
was published in 1978. The concept of asymmetric encryption was first
introduced by Whitfield Diffie \index{Diffie Whitfield}  and Martin
\index{Hellman Martin} Hellman in 1976. Today, the ElGamal \index{ElGamal}
procedures also play a decisive role, particularly the \index{Schnorr} Schnorr
variant in the \index{DSA} DSA (Digital \index{Signatures!digital}Signature
Algorithm).

>>>>

% --------------------------------------------------------------------------
\subsubsection{New results about cryptanalysis of AES}
\index{Cryptanalysis} \label{NeueAES-Analyse}

@@

% --------------------------------------------------------------------------
\subsubsection{Current status of brute-force attacks on 
symmetric algorithms (RC5)}
\index{brute-force attack}
\index{RC5}
\label{Brute-force-gegen-Symmetr}

@@

The most well-known asymmetric procedure is the \index{RSA} 
RSA algorithm\index{CrypTool}%
\footnote{%
The RSA algorithm is extensively described in chapter 3.10 and later
within this script. 
The RSA cryptosystem can be executed in many variations with 
CrypTool\index{CrypTool} v1.3 (using the menu 
{\bf Individual Procedures \textbackslash{} RSA Demonstration \textbackslash{}
RSA Cryptosystem}). 
The topical research results concerning RSA are described in chapter 3.11.
}%
,
named after its developers Ronald \index{Rivest Ronald} Rivest, Adi
\index{Shamir Adi} Shamir and Leonard \index{Adleman Leonard} Adleman. The RSA algorithm
was published in 1978. The concept of asymmetric encryption was first
introduced by Whitfield Diffie \index{Diffie Whitfield}  and Martin
\index{Hellman Martin} Hellman in 1976. Today, the ElGamal \index{ElGamal}
procedures also play a decisive role, particularly the \index{Schnorr C.P.} Schnorr
variant in the \index{DSA} DSA (Digital \index{Signatures!digital}Signature
Algorithm).

### 2003-05-23 script/en/chapters/introduction.tex
Änderungen Esslinger
be update

In order to also enable developers/authors to work together independently 
the topics have been split up and for each topic an extra chapter has been 
written which can be read on its own. The later editorial work in TeX added 
cross linkages between different sections and footnotes describing where you
can find the according functions within the CrypTool\index{CrypTool} 
program (see menu tree in appendix A). 
% \hyperlink{appendix-menutree}{(see menu tree in appendix A).}
% in \ref{s:appendix-menutree}
% \hypertarget{appendix-menutree}{}\label{s:appendix-menutree}
Naturally there are much more interesting topics in mathematics and
cryptography which could be discussed in greater depth -- therefore this
is only one of many ways to do it.

@@

This edition of the script mainly updates the summaries of the following 
topical research areas:
\vspace{-7pt}
\begin{itemize}
  \item the search for the largest prime numbers (generalized Mersenne 
        and Fermat primes) \\ (chap. 2.6), 
  \item progress in number theory ("Primes in P") (chap. 3.11.3), 
  \item the factorisation of big numbers (TWIRL) (chap. 3.11.3),
  \item progress in cryptanalysis of the AES standard (chap. 1.1.1) and
  \item progress in brute-force attacks against symmetric algorithms (chap. 1.1.2).
\end{itemize}

@@

Frankfurt, March 2003

@@

Chapters 4 and 6 might require a deeper knowledge in mathematics, while the
other chapters should be understandable with a school leaving certificate.

@@

CrypTool\index{CrypTool} was developed during the end-user awareness program
at Deutsche Bank in order to increase employee awareness of IT security and provide them with
a deeper understanding of the term security.\par \vskip + 3pt

A further aim has been to enable users to understand the cryptographic
procedures. In this way, using CrypTool
as a reliable reference implementation of the various encryption procedures
(because of using the industry-proven Secude Library\index{Secude}),
you can test the encryption implemented in other programs. \par \vskip + 3pt

@@

>>>>

In order to also enable developers/authors to work together independently 
the topics have been split up and for each topic an extra chapter has been 
written which can be read on its own. The later editorial work in TeX added 
cross linkages between different sections and footnotes describing where you
can find the according functions within the CrypTool\index{CrypTool} 
program (see menu tree in appendix A). 
% \hyperlink{appendix-menutree}{(see menu tree in appendix A).}
% in \ref{s:appendix-menutree}   AUFPASSEN, DASS nichts doppelt !!
% \hypertarget{appendix-menutree}{}\label{s:appendix-menutree}
Naturally there are much more interesting topics in mathematics and
cryptography which could be discussed in greater depth -- therefore this
is only one of many ways to do it.

@@

This edition of the script mainly updates the summaries of the following 
topical research areas:
\vspace{-7pt}
\begin{itemize}
  \item the search for the largest prime numbers (generalized Mersenne 
        and Fermat primes) \\ (chap. \ref{spezialzahlentypen}), 
  \item progress in number theory (``Primes in P'') (chap. \ref{PrimesinP}), 
  \item the factorisation of big numbers (TWIRL, RSA-160) 
        (chap. \ref{TWIRLDevice}, \ref{RSA-160}),
  \item progress in cryptanalysis of the AES standard 
        (chap. \ref{NeueAES-Analyse}) and
  \item progress in brute-force attacks against symmetric algorithms 
        (chap. \ref{Brute-force-gegen-Symmetr}).
\end{itemize}

@@

Hofheim, May 2003

@@

Chapters 4 and 6 require a deeper knowledge in mathematics, while the
other chapters should be understandable with a school leaving certificate.

@@

CrypTool\index{CrypTool} was developed during the end-user awareness program
at Deutsche Bank in order to increase employee awareness of IT security and provide them with
a deeper understanding of the term security.
A further aim has been to enable users to understand the cryptographic
procedures. In this way, using CrypTool
as a reliable reference implementation of the various encryption procedures
(because of using the industry-proven Secude Library\index{Secude}),
you can test the encryption implemented in other programs. \par \vskip + 3pt

@@

Hofheim, May 2003

### 2003-05-23 script/en/chapters/moderncryptography.tex
be update

In this process, we describe a problem as ``easy'' if it can be solved in 
\index{Runtime!polynomial} polynomial time as a function of the length of the 
input. If the length of the input is $ n $ bits, then the time for calculating 
the function is proportional to $ n^{a}, $ where $ a $  is a constant. We say 
that the \index{Complexity} complexity of such problems is $ O(n^{a}) $
[Landau- or Big-O notation].

@@

The term ``practically impossible'' is slightly less precise. In 
general, we can say that a problem cannot be solved \index{Runtime!efficient} 
efficiently, if the time required to solve it increases more quickly than the 
polynomial time as a function of the size of the input. If, for example, the 
length of the input is $ n $  bits and the time required for calculating the 
function is proportional to $ 2^n $, then the following currently applies: the 
function practically cannot be calculated for $n > 80$.

@@

    \item The class \textbf{P}: This class contains those problems that can be 
solved in a polynomial amount of time.

		\item The class \textbf{NP}: The definition of this class doesn't look at
		the time required to solve a problem, but rather at the time required to
		verify a given solution. The class \textbf{NP} consists of those problems
		for which a given solution can be verified in a polynomial amount of time.
		Hereby, the term \textbf{NP} ``non-deterministic'' means polynomial and is
		based on a calculation model, i.e. on a computer that only exists in theory
		and can ``guess'' correct solutions non-deterministically then verify them
		in polynomial time.

@@

The class \textbf{P} is contained in the class \textbf{NP}. A well-known 
unsolved problem is the question whether or not $ \textbf{P} \neq \textbf{NP} $ 
is true, i.e. whether or not \textbf{P} is a true subset. An important property 
of the class \textbf{NP} is that it also contains what are known as ``\textbf{NP}-complete''
problems. These are problems that represent the 
class \textbf{NP} as follows: If a ``good'' algorithm for such a 
problem exists, then ``good'' algorithms exist for all problems from 
\textbf{NP}. In particular: if \textbf{P} only contained one complete problem, 
i.e. if a polynomial solution algorithm existed for this problem, then 
\textbf{P}would be equal to \textbf{NP}. In this sense, the \textbf{NP}-complete 
problems are the most difficult problems in \textbf{NP}.

@@

A number of algorithms have been suggested for public key procedures\index{Cryptography!public key}. In many 
cases - although they at first appeared promising - it was discovered that they 
could be solved polynomially. The most famous failed applicant is the knapsack 
with trapdoor, suggested by Ralph Merkle \cite{Merkle1978}.

@@

You are given $ n $ objects $ G_1, \dots, G_n $ with the weights $ g_1, \dots 
g_n $ and the values $w_1, \cdots, w_n. $ The aim is to carry away as much as 
possible in terms of value while restricted to an upper weight limit $ g $. You 
therefore need to find a subset of $ \{ G_1, \cdots,G_n\}, $ i.e. $ \{G_{i_1}, 
\dots ,G_{i_k} \}, $ so that $ w_{i_1}+ \cdots +w_{i_k} $ is maximised under the 
condition $  g_{i_1}+ \cdots +g_{i_k} \leq g. $ \par
Such questions are called {\bf NP}-complete problems (not \index{Runtime!not polynomial NP} deterministically polynomial) that are difficult to 
calculate.\index{Knapsack}

@@

In 1982, \index{Shamir Adi} Shamir \cite{Shamir1982} specified an algorithm for 
breaking the system in polynomial time without solving the general knapsack 
problem. Len \index{Adleman Leonard} Adleman \cite{Adleman1982} and Jeff 
Lagarias \index{Lagarias Jeff} \cite{Lagarias1983} specified an algorithm for 
breaking the twice iterated Merkle-Hellman knapsack encryption procedure in 
polynomial time. Ernst Brickell \index{Brickell Ernst} \cite{Brickell1985} then 
specified an algorithm for breaking multiply iterated Merkle-Hellman knapsack 
encryption procedures in polynomial time. This made this procedure unsuitable as 
an encryption procedure. It therefore delivers a one way function whose trapdoor 
information (defamiliarisation of the 0-1 knapsack problem) could be discovered 
by an evesdropper.

>>>>

In this process, we describe a problem as ``easy'' if it can be solved in 
\index{Runtime!polynomial} \index{Polynomial }polynomial time as a function of the length of the 
input. If the length of the input is $ n $ bits, then the time for calculating 
the function is proportional to $ n^{a}, $ where $ a $  is a constant. We say 
that the \index{Complexity} complexity of such problems is $ O(n^{a}) $
[Landau- or Big-O notation].

@@

The term ``practically impossible'' is slightly less precise. In 
general, we can say that a problem cannot be solved \index{Runtime!efficient} 
efficiently, if the time required to solve it increases more quickly than the 
polynomial \index{Polynomial }time as a function of the size of the input. If, for example, the 
length of the input is $ n $  bits and the time required for calculating the 
function is proportional to $ 2^n $, then the following currently applies: the 
function practically cannot be calculated for $n > 80$.

@@

    \item The class \textbf{P}: This class contains those problems that can be 
solved in a polynomial \index{Polynomial} amount of time.

		\item The class \textbf{NP}: The definition of this class doesn't look at
		the time required to solve a problem, but rather at the time required to
		verify a given solution. The class \textbf{NP} consists of those problems
		for which a given solution can be verified in a polynomial \index{Polynomial} amount of time.
		Hereby, the term \textbf{NP} ``non-deterministic'' means polynomial and is
		based on a calculation model, i.e. on a computer that only exists in theory
		and can ``guess'' correct solutions non-deterministically then verify them
		in polynomial time.

@@

The class \textbf{P} is contained in the class \textbf{NP}. A well-known 
unsolved problem is the question whether or not $ \textbf{P} \neq \textbf{NP} $ 
is true, i.e. whether or not \textbf{P} is a true subset. An important property 
of the class \textbf{NP} is that it also contains what are known as ``\textbf{NP}-complete''
problems. These are problems that represent the 
class \textbf{NP} as follows: If a ``good'' algorithm for such a 
problem exists, then ``good'' algorithms exist for all problems from 
\textbf{NP}. In particular: if \textbf{P} only contained one complete problem, 
i.e. if a polynomial \index{Polynomial} solution algorithm existed for this problem, then 
\textbf{P}would be equal to \textbf{NP}. In this sense, the \textbf{NP}-complete 
problems are the most difficult problems in \textbf{NP}.

@@

A number of algorithms have been suggested for public key procedures\index{Cryptography!public key}. In many 
cases - although they at first appeared promising - it was discovered that they 
could be solved polynomially\index{Polynomial}. The most famous failed applicant is the knapsack 
with trapdoor, suggested by Ralph Merkle \cite{Merkle1978}.

@@

You are given $ n $ objects $ G_1, \dots, G_n $ with the weights $ g_1, \dots 
g_n $ and the values $w_1, \cdots, w_n. $ The aim is to carry away as much as 
possible in terms of value while restricted to an upper weight limit $ g $. You 
therefore need to find a subset of $ \{ G_1, \cdots,G_n\}, $ i.e. $ \{G_{i_1}, 
\dots ,G_{i_k} \}, $ so that $ w_{i_1}+ \cdots +w_{i_k} $ is maximised under the 
condition $  g_{i_1}+ \cdots +g_{i_k} \leq g. $ \par
Such questions are called {\bf NP}-complete problems (not \index{Runtime!not polynomial NP} deterministically polynomial\index{Polynomial}) that are difficult to 
calculate.\index{Knapsack}

@@

In 1982, \index{Shamir Adi} Shamir \cite{Shamir1982} specified an algorithm for 
breaking the system in polynomial \index{Polynomial} time without solving the general knapsack 
problem. Len \index{Adleman Leonard} Adleman \cite{Adleman1982} and Jeff 
Lagarias \index{Lagarias Jeff} \cite{Lagarias1983} specified an algorithm for 
breaking the twice iterated Merkle-Hellman knapsack encryption procedure in 
polynomial time. Ernst Brickell \index{Brickell Ernst} \cite{Brickell1985} then 
specified an algorithm for breaking multiply iterated Merkle-Hellman knapsack 
encryption procedures in polynomial time. This made this procedure unsuitable as 
an encryption procedure. It therefore delivers a one way function whose trapdoor 
information (defamiliarisation of the 0-1 knapsack problem) could be discovered 
by an evesdropper.
